\vbox{

\subsection*{A Fire Within}

{\color{violet} \faPalette} Jack Regal

{\color{teal} \faMapMarked} Space Dome

The inspiration behind this art piece is that we all have a fire burning in us. Drive, focus, love, motivation, inspiration, what ever it may be we all have a fire inside of us. My hope is that this piece will be a reminder to people to keep the fire within themselves stoked and burning.

}



\vbox{

\subsection*{Angie’s Heart}

{\color{violet} \faPalette} Mark “Swizee” Switzer

Angie’s Heart is small but powerful just like the woman it was named after. Watch her fire burn!

}



\vbox{

\subsection*{Arborealis}

{\color{violet} \faPalette} JJ Knottinghill

Arborealis....The Fire Tree..... Rope, Fuel, Fire.

}



\vbox{

\subsection*{Big Brother}

{\color{violet} \faPalette} Lee Lukasek

{\color{teal} \faMapMarked} Little Bohemia



}



\vbox{

\subsection*{Blue Ghost}

{\color{violet} \faPalette} Ben Stewart

{\color{teal} \faMapMarked} The Broken Drum

Inspired by the blue ghost and synchronous fireflies surrounding Asheville.



It's rumored that the Blue Ghosts have learned a thing or two on their journey to the moon. Can they hear you? Are they following you? Is it all in your head man? Just be careful not to spook them.

}



\vbox{

\subsection*{Boba's Bar Barge}

{\color{violet} \faPalette} Joshua Boyer

Boba's is your libation station in the middle of the lake! Come out and have a cocktail or mocktail with us while you're cooling off! You know how it works. Bring your own cup!

}



\vbox{

\subsection*{Bubbles and Bass}

{\color{violet} \faPalette} Gabi "Nectar"

Come experience a lakeside lunar rendition of Bubbles and Bass! From the playa To The Moon, we give you the ultimate daytime party place.

}



\vbox{

\subsection*{Burner Bingo}

{\color{violet} \faPalette} Drunk Christine

{\color{teal} \faMapMarked} Burntastic Barbie

Get to know new folks… Interactive scavenger hunt to find burners that fill out your bingo card. Pick up your bingo sheet and pen, write your name so it doesn’t get mooped, find burners who fit the description, get BINGO and return for swag pin!

}



\vbox{

\subsection*{Burntastic Barbie Theme Camp}

{\color{violet} \faPalette} Drunk Christine

{\color{teal} \faMapMarked} Burntastic Barbie

Come play with a doll sized burn and take one along for more adventures!



What We Hope Our Art Will Help You Do:



Experience participation through immediacy with art. 



Explore our burn culture through both a reflective and projective lens. 



Facilitate empathy through intentional narrative play. 



Engage in collective nostalgia of a shared zeitgeist past and present. 



And ultimately just enjoy… because silliness, fun, play, and curiosity are powerful connections to our deeper humanity.

}



\vbox{

\subsection*{CATstronaut}

{\color{violet} \faPalette} Andy "Raptor" Berres

{\color{teal} \faMapMarked} Survival Guide

Once upon a time, a shaggy tuxedo cat snuck onto the wing of an airplane to hitch a ride. In recognition of this bravery and celebration of their safe return to ground, this cat is featured on this year's Survival Guide cover. \faCat

}



\vbox{

\subsection*{Creature Cabinet}

{\color{violet} \faPalette} Citrus Blossom

{\color{teal} \faMapMarked} The Black Lodge

Leave No Trace meets Radical Self-expression in this integrative peice of art. Try opening the doors of reality to see into someone else's perspective.

}



\vbox{

\subsection*{Daphne}

{\color{violet} \faPalette} Danielle Cain

Daphne is a propane driven German folk wind spinner goddess muse. A delicate Fucking Flower.

}



\vbox{

\subsection*{Every Burn Carry}

{\color{violet} \faPalette} Anna Bane

{\color{teal} \faMapMarked} Camp Just People

It’s like EDC (Every Day Carry), except at a burn. We’ve got bottles, pouches, straps, keyrings, carabiners … Do you find yourself wishing you had more pockets? Choose a pre-made solution, or we can even make you something, such as a a custom ribbon sling - choose your own color and length! We also have paint markers to personalize and/or de-commodify. Come by Camp Just People and we’ll help you figure out a better on-body logistical situation!

}



\vbox{

\subsection*{Fire-Flowers}

{\color{violet} \faPalette} Kuz

Fire-Flowers! A pair of tempered glass encased fire vortexes! Made from reclaimed materials … Fire-Flowers where reborn from what was left behind! Inspired by the light in our flames, we seek another, our Dual - Flames! Our “ Fire -Flower”! We welcome you, to hold back the darkness with us! 

{\color{red} \faIcon{fire-alt}} {\color{pink} \faSpa}  Cheers!

}



\vbox{

\subsection*{FreeRange Disco}

{\color{violet} \faPalette} Paula Happens

FreeRange Disco is a silent disco that is a roaming installation, playing music and other things from participating camps

}



\vbox{

\subsection*{Giving dragon}

{\color{violet} \faPalette} Lee Lukasek

{\color{teal} \faMapMarked} Little Bohemia

Giving Dragon a small creature to exchange gifts throughout on the Burn. It is a must to leave a gift to re9a gift. Of course if you just want to donate the Giving Dragon will find a Burner in need.

}



\vbox{

\subsection*{Golden Gleam}

{\color{violet} \faPalette} Ayla “Asher” Hamilton

{\color{teal} \faMapMarked} Splashy Splashy Water Camp, AKA Lake

Come to the Lake and paddle in an umbrella boat - a recreation from the boat scene from Cirque du Soleil's movie "World's Away".  Umbrella boats will accomidate 1-2 humans.

}



\vbox{

\subsection*{Hammock City}

{\color{violet} \faPalette} Tal Peretz

Hammock City! has become a favorite chill space for so many people; a great oasis to escape all the noise and lights and just relax, draw, sing, paint, and make new friends.

}



\vbox{

\subsection*{Keyhole Portal to Curiosity}

{\color{violet} \faPalette} Isaac Blaxton

Come and peer through the portal, and entertain the realm of the possible! The more curious you become, the bigger the reward. Hidden along your journey are untold treasures, left behind by previous travelers. Let your curiosity take wing, find a key, and cross through the portal. Join us on a journey to the more curious side of life, there just may be a reward.

}



\vbox{

\subsection*{Little Bohemia Owl}

{\color{violet} \faPalette} Lee Lukasek

{\color{teal} \faMapMarked} Little Bohemia

Little Bohemia Owl is coming home where it was born.

}



\vbox{

\subsection*{Me, Myself \& I}

{\color{violet} \faPalette} Jason The Virgin \& MoniWack

{\color{teal} \faMapMarked} Headroom/mobile

Me, Myself \& I -- Two life sized mobile marionettes (one set is feminine and one set is masculine) dancing with me who can interact with friendly participants that are encouraged to hug, conga or dance along to share in the fun as we roam about.

}



\vbox{

\subsection*{Moon Shuttles}

{\color{violet} \faPalette} Acrodesiac Lunartics Tribe

{\color{teal} \faMapMarked} Front gate or ice station

Our exquisitely decorated, durable Moon Shuttles are available for all lunatics to haul gear to their campsites, pick top ice for their camp, deliver gifts, and move things around the burn.  Located near the gate, Moon Shuttles can be bororrowed at anytime. We kindly ask that Shuttles are returned to the Station when not used so other can use them.

}



\vbox{

\subsection*{Planetarium Aquarium}

{\color{violet} \faPalette} Gene Dolan

{\color{teal} \faMapMarked} Camp Just People

Will take you into deep space and deep sea with our visual projections

}



\vbox{

\subsection*{Purpureus}

{\color{violet} \faPalette} Greg Ignasiak

Purpureus is a glowing towering flower sculpture which draws people like pollinators to it's climbable leaves, creating a vibrant space for playful activity and gatherings.

}



\vbox{

\subsection*{Rocket ship poofers}

{\color{violet} \faPalette} Lee Lukasek

{\color{teal} \faMapMarked} Little Bohemia



}



\vbox{

\subsection*{Secret Sacred Space Time Portal}

{\color{violet} \faPalette} Andrea Kersn

Pay attention to the clues, maps, keys and hints you may come across during the burn, as they just might lead you to the Secret Sacred Space Time Portal at a time just right for you ~ to come across a very special sonic ceremony in a very special spot on this magical land. 

(for safety reasons, children under 18 are unfortunately not able to join)

}



\vbox{

\subsection*{Solar System on the Moon}

{\color{violet} \faPalette} Andy "Raptor" Berres

{\color{teal} \faMapMarked} Department of Synergy

Our Solar System has a lot of really cool planets. Can you find them all and return a flag to the moon? This is an interactive scavenger hunt to encourage you to visit theme camps and make friends. If you find all the planets and sign into the log book, you will get a cool patch.

}



\vbox{

\subsection*{Talk to God}

{\color{violet} \faPalette} Jaye Hersh

Talk to God comes from Black  Rock City To the Moon! Bring your questions and concerns to the Booth, or sit in the Throne and *be* the Deity! Serious, silly, snarky, compassionate, whatever happens, is the real deal.

}



\vbox{

\subsection*{Tessrekt}

{\color{violet} \faPalette} Scott Marcus

How many LEDs can fit inside a 1 foot cube from another dimension? Let's find out! I also heard you liked cubes so we put a cube inside a cube. It's cubes all the way down.

}



\vbox{

\subsection*{The Caterpillar \& the MoonFlower}

{\color{violet} \faPalette} OuijaCat

Enjoy the mystical allure of The MoonFlower as glowing flowers, mandalas, mushrooms, \& magical creatures beckon you to sit/stay. Plenty of daylight surprises. Come interact with Absolem, the Blue Caterpillar. Feel like a picnic? Bring a snack/drink/skill to share with/entertain anyone passing by.  Find a wish to grant/leave a wish for others to grant. Do a little arts and crafts at home and make you own small flower/magical creature to add to the mix. Make it glow… Make it pop… Make it MAGICAL!

}



\vbox{

\subsection*{The Fur Wall}

{\color{violet} \faPalette} Tape

The Fur Wall is a visual and tactile experience consisting of a 7'x7' wall of thousands of LEDs diffused by a soft white faux fur. Come on by to either watch as it cycles through a series of patterns, or walk up and pet the wall for some extra sensory fun!

}



\vbox{

\subsection*{The Gifting Tree}

{\color{violet} \faPalette} OuijaCat

Practice the Principle of \textbf{Gifting} - bring your offerings to the Gifting Tree.

Through the sharing of food, music, conversation, artistic talents, something from our lives that we are ready to part with, or ourselves through \textbf{Radical Participation} and \textbf{Radical Self Expression}, a “gift” is an opportunity for both giver and receiver to gain pleasure from the exchange and the \textbf{Immediacy} of the moment, without expectation.

Come once… come often.

}



\vbox{

\subsection*{The Hypercube}

{\color{violet} \faPalette} Austin Waycaster/Spectral Subverse

{\color{teal} \faMapMarked} Spectral Subverse

Come take a glance for a while, or maybe get lost for an eternity. The Hypercube beckons; are you listening? Come dance, sit and play around this infinity mirror cube found at the heart of the Spectral Subverse.

}



\vbox{

\subsection*{The Pocket Dimension Waystation}

{\color{violet} \faPalette} Christina Cureton

{\color{teal} \faMapMarked} The Black Lodge

The Pocket Dimension Waystation allows you to travel to over a dozen tiny worlds, each unique, and interactive! The Dimensional Wonders contain countless things to see and do! The most important part of the Waystation- PLAY. If you can SEE it, you can TOUCH IT. If you can TOUCH IT- PLAY WITH IT. Lose yourself in creating stories for these worlds. Will you see joy, while another writes a tale of tragedy? How will you combine the elements? No way to know, unless you let go, and dive on in....

}



\vbox{

\subsection*{The Totally Not Mad Hatter's Tea Party}

{\color{violet} \faPalette} Corey Pennington

{\color{teal} \faMapMarked} ImagiNation

The Totally Not Mad Hatter's Tea Party will be a space of themed changeable decorations t and  table to come visit, sit a while and enjoy tea and or brunch.

}



\vbox{

\subsection*{The Trading Booth}

{\color{violet} \faPalette} Andrew Weaver

Are you ready to explain the value of your trade to The Broker? Upon approval from The Broker the trading booth items are traded, “take one, leave one”. Make your case.



The Trading Booth will not support the trades of alcohol or drugs of ANY kind. 

All food \& non-alcoholic beverages must be in original packaging AND sealed.



Come visit The Broker. Let’s make a deal.

}



\vbox{

\subsection*{The Twin Poofers}

{\color{violet} \faPalette} Jack Regal

{\color{teal} \faMapMarked} Space Dome

One of my favorite things to do at a burn is push the button on poofers. It brings me a type of childlike joy that I can't describe. I want to share this joy with others. My poofers are remote controlled so I will be able to let many different people have the opportunity to push the button and experience that joy.

}



\vbox{

\subsection*{The Un-Principles}

{\color{violet} \faPalette} Anna Bane

{\color{teal} \faMapMarked} Camp Just People

Come vote for the Un-Principles! Which are NOT in opposition to the Principles; rather, they're the things that happen despite how well you follow the Principles. They attest to the travails of the rest of the burn experience, and you get to choose which are your favorites! We also love the 10+1 Principles themselves, and you can read more about them here, too; get a drink at Camp Just People’s bar and let's have a lively discussion!

}



% \vbox{

% \subsection*{The art project is "Talk to God"}

% {\color{violet} \faPalette} Jaye Hersh



% }



\vbox{

\subsection*{Through the Looking Glass}

{\color{violet} \faPalette} Elissa Morris

{\color{teal} \faMapMarked} Headroom

A secret clearing where all is reflected. Mirrors hanging in the trees give glimpses of another world. The centerpiece, Alice, is a life-sized statue covered in mirror tiles. She reflects the beauty of nature around her. During the day, the clearing is a space of reflection, a place to wonder at the natural beauty that surrounds you. At night, hundreds of tiny LEDs illuminate the space, spotlights reflect against the mirrors, turning the space into a disco.

}



\vbox{

\subsection*{Tree Star City}

{\color{violet} \faPalette} Trinity White

{\color{teal} \faMapMarked} Camp PFA

Tree Star City is interactive as an explorable art piece, where burners will have all of their senses sparking in immersive spaces amongst the forest.  Astronauts can take space walks and chill on tentsile hammocks, swing into space in a parachute, or lounge on a lunar landing pad. We hope you all get lost in space with us!

}



\vbox{

\subsection*{Zoltar's Wishing Booth and Odditorium}

{\color{violet} \faPalette} OuijaCat

Come by Zoltar’s and have your fortune told, make a wish, play Truth or Dare, consult the Magic 8 Ball, or just get some good (or bad) advice. Just be careful what you wish for.  Don’t ask for anything too “Big.” 

Would you like to participate/entertain? Can you tell fortunes, belly dance, or perform cool tricks? Do you have a snazzy outfit and would you like to be Zoltar for an hour or two. Contact me or sign up at the booth. Add a freak to The Odditorium – make one at home or draw one onsite.

}



