%
% Here are the many ways folks can help out.
%
% TODO I know I'm missing lots.  :-\
%

\chapter{Volunteering}
\label{ch:volunteering}

% This is true if only doing the flight manual, not the pre-flight
% \ifisflight
%   % This one page needs to be one column to look right, even
%   % in the flight manual, proper.
%   % failed experiment to add thumb guides
% %   \addthumb{Welcome}{}{white}{black}
% \putchapterthumb
% \fi

No burn exists without volunteers and volunteers are our heroes! We have no hired help other than security and everything we do is done on a volunteer basis.  This goes for all the things before, during, and after the burn.  All the teams that you can volunteer for are described in the ``Crew Manifest'' section starting from page \pageref{ch:teams}.

There are two ways to volunteer:

\textbf{Before the event} you can sign up from the available volunteer activities by going to:

{\indent ~~~ \url{https://www.signupgenius.com/tabs/33773df01a4c3edc42-tothemoon} }

\textbf{During the event} you can go to the \gls{vc} folks at the \gls{cockpit} to sign up for an available volunteer slot.

\section*{EARLY ENTRY FOR VOLUNTEERS}

If a participant has a volunteer shift on Wednesday, they will be granted entry at noon on Wednesday.\footnote{This is mainly \gls{gate} but a few other teams have a few volunteer shift scheduled for Wednesday for set up.}  If a participant has a volunteer shift beginning before noon on Thursday they will be granted early entry on Wednesday.  This list will be given to \gls{gate} from \gls{vc} before \gls{gate} opens opens on Wednesday.

All participants must be off site by noon on Monday unless they have a shift on Monday after noon. In which case they will need to have permission from \gls{vc} or one of the \gls{eventleads} to stay on site for that shift, and should stop by the \gls{vc} tent on Monday before 10 am to get their approval. All late stay volunteer must also have their camp packed before their shift on Monday and be prepared to leave immediately following that last shift.\footnote{There are other early entries granted for \glspl{themecamp}, \gls{dpw}, \glspl{teamleads}, \gls{bod}, etc,,  but those lists will be given to \gls{gate} from appropriate lead for that team. This info is just for those volunteering first shifts on teams that start when gates open or before.}


% \clearpage
\section*{Volunteer Training}

\subsection*{Conclave}
We ask that all fire performers attend one of the fire safety meetings to obtain a wristband, which allows you to spin fire at theme camps hosting fire circles.

Fire Safety meetings will be at the Effigy in the Burn Field. Spinners in Conclave must attend one of the training events listed below. You will be given a fire safe wristband to spin fire during the duration of the burn. Conclave Participants will also meet at \gls{effigyburnfield} at 2:00\pm{} Saturday afternoon, and again at 7:00\pm{} for curtain call.

\begin{center}
\footnotesize
\begin{tabular}{|c|c|c|}
\hline
\textbf{Day} & \textbf{Time} & \textbf{Place} \\ \hline
Friday & 7\pm{} &  Effigy Burn Field  \\ \hline
Saturday & 2\pm{} & \gls{effigyburnfield}  \\ \hline
Saturday & 7\pm{} & \gls{effigyburnfield}  \\ \hline
\end{tabular}
\end{center}

\subsection*{Greeters}

We are looking for outgoing, space-age, creative people to join our band of misfits.  If you are dedicated, patient, have great communication skills, and are ready to take on the truly awesome role of creating out-of-this-world merriment and moon-like magic, then volunteer with us. 

See you on the Moon!!!!

The \glspl{greeter} meet at the \gls{launchpad}.


\subsection*{Perimeter}
Outer Perimeter volunteers meet at the \gls{effigyburnfield} on before the burn time and establish a burn perimeter to aid in the safety of participants during the burn.\textbf{ Training for these volunteers is mandatory.}

Outer Perimeter meet 3\pm{} on Saturday for training, no experience needed.
Inner perimeter meet 4\pm{} on Saturday for training, and you \textit{must be experienced}. Temple meet 3\pm{} on Sunday for training.

If you are experienced with perimeter and fire safety and want a shift doing \textbf{inner} perimeter, please email the perimeter lead directly (\url{perimeter@tothemoonburn.com}) and they will vet you for that.

\begin{center}
\footnotesize
\begin{tabular}{|c|c|c|}
\hline
\textbf{Day} & \textbf{Time} & \textbf{Place} \\ \hline
Saturday & 3\pm{} & \gls{effigyburnfield} \\ \hline
Saturday & 4\pm{} & \gls{effigyburnfield} \\ \hline
Sunday & 3\pm{} & \gls{templefield} \\ \hline
\end{tabular}
\end{center}

\subsection*{Rangers and Fire Safety}

\begin{center}
\footnotesize
\begin{tabular}{|c|c|c|}
\hline
\textbf{Day} & \textbf{Time} & \textbf{Place} \\ \hline
Thursday & 7\pm{} & \gls{moonrangerstation} \\ \hline
Friday & 1\pm{} & \gls{moonrangerstation} \\ \hline
\end{tabular}
\end{center}


% \newpage
\vbox{
\subsection*{Tbase / Sanctuary}
\label{sec:tbase-training}
Please plan to attend one of the virtual training sessions on online prior to the burn. You can register for on the virtual classe via google form via this link: \href{https://docs.google.com/forms/d/e/1FAIpQLScqsj6QH1fEJZKUIxOGaP301ZAJBM50pTmnlwepkWp8rYpBIw/viewform}{TBASE Training Registration}.

There are no tbase trainings on site, though if you haven't done the online training, the shift lead will do so with individual volunteers. The final online training is at 6pm on June 17th. 


% \begin{center}
% \footnotesize
% \begin{tabular}{|c|c|c|}
% \hline
% \textbf{Day} & \textbf{Time} & \textbf{Place} \\ \hline
% Thursday & 5\pm{} & \gls{tbass} \\ \hline
% Friday & 5\pm{} & \gls{tbass} \\ \hline
% \end{tabular}
% \end{center}

}

\subsection*{Traffic}

Help Lunartics get to their landing pads in an orderly fashion! Make sure the flow of vehicles is going the correct direction, hold the line to minimize the flustercucks, and be amongst the first faces to welcome in the masses! Work closely with Parking and Greeters to ensure the smoothest entry and exit To The Moon! For your Traffic shift grab any obnoxious noise makers and lights you have to keep the attention on YOU, you little traffic star, and head to the \gls{vc} tent to get picked up for your shift! *shady swag provided*

% \bod[inline]{add all volunteer training}
% \todo[inline]{Add information on how to volunteer before and during the event. Probably from https://www.tothemoonburn.com/volunteering}



\newpage
\subsection*{Notes}

Note down your training here!


\vspace{2.5in}

\subsection*{Volunteer Shifts}

Note down you volunteer shifts here!