%
% Part of the reason why we go to burns, AMIRIGHT?
%

\chapter{Art}

% This is true if only doing the flight manual, not the pre-flight
\ifisflight
  % This one page needs to be one column to look right, even
  % in the flight manual, proper.
  % failed experiment to add thumb guides
%   \addthumb{Welcome}{}{white}{black}
\putchapterthumb
\fi
% I commented out the old formatting.
% \section*{Funded Art}

% \subsection*{Temporary Placeholder}

% \section*{Funded Burn Art}

% \subsection*{Temporary Placeholder}

\section*{Ancient Mysteries}
An 80' wide by 10' tall ancient mysteries mural by Dima Yastronaut. It will illustrate ancient architectural sites such as mythological gods and creatures throughout all of history, architectural sites, pyramids and sacred temples from around the world. Compiled together with thousands of layers of ancient history, sacred geometry and symbolism.

\section*{BAR[ge]}
Avast ye scurvy landlubbers, step on board and get ready to set sail on the maiden voyage of the BAR[ge]. This year, the Clinch river will be more naughty and nautical then ever before! Join us for refreshments, sing along with our BARgetenders' favorite chanties, plunder the booty and heave-ho three sheets to the wind!



\section*{Blacklight creation cave }
The blacklight bubble cave is a replica of a real-life cave, protected by the Dogon tribe in Africa. Paintings displayed on the cave walls were received from a mysterious group of fish-like people (Nammo) who came in from the sky and landed in a lake, there on the doorstep of this tribe to share their wisdom of the universe and their home star system. We are lucky enough to have this wisdom at The Moon this year, and through technological miracles, we have constructed a blacklight wormhole tunnel to ping you up to Sirius B to ask the Nammo yourself about the wonders of the universe ;) 

\section*{Comet in Stasis}
A suspended sphere of glowing, pulsating lights encased in ice, the Comet in Stasis brings the a cool, refreshing presence to the Moon. This project consists of a robust stand and a ball of ice that is replaced every night. The ball of ice (Comet) itself is 1 foot in diameter with LEDs embedded in the center. It hangs suspended at chest level from a chain. The LEDs in the center of the Comet pulse with otherworldly patterns, attracting lunar-tics from all across the Moon's surface. Once enthralled by the Comet's otherworldly glow, burners can touch and play with the ball of ice, offering a reprieve from the heat of the lunar surface.


\section*{Cafe Burns Misting Station}
Cooling Misting Station 


\section*{Dear Future Me,}
I will lay out paper, pens, and envelopes and will ask people to write a letter to themselves, which they will then enclose in an envelope and place in a box. I will then mail all of the letters out at an undisclosed future date! Surprise yourself with a blast from the past! 

\section*{Fairy Circus}
Coming from Hollywood Florida The Fairy circus is a 24ft aerial rig decorated with different colored fabrics. At the top of the aerial rig we will have different kinds of ivy and flowers hanging to make it magical. will be doing aerial silks performances every night and teaching aerial silks during the day and I have insurance for both. Kassi Abreu will be performing on her Lyra every night as well as any other aerialist who want to play. We really love what we do and being able to share it with so much love! 


\section*{Filia}
Filia is a crystal grid, named for the Greek word for friendship. With a total of seven points there will be podium style stands which will hold beautiful large examples of each crystal and a placard explaining the grid which point you are at and where others points of the grid are located. They will be lit up at night. The friendship crystal grid is made up of three different types of crystals citrine, amazonite, and carnelian. Smoky Citrine (the focus stone)will help to attract good earth energies. Amazonite (the way stone) will bring us understanding and open mindedness. Carnelian (the desire stone) will bring loyalty faithfulness and support. This grid is known as the Borromean rings which is the design of stabilization and unity. This design will work well with our placement as all points will be placed along the roadside of the already existing roads at TTM. It just so happens the shape of this grid is diviningly a perfect shape!




\section*{Gerlach The Friendly Triffid}
If you see wriggling and curling tentacles, you'll know you've found Gerlach The Friendly Triffid. Everything it does is automated. The only human input is from you. 


\section*{Hammock City! }
A peaceful place to hammock and recharge. 

\section*{Kinesios}
40'-0" tall Burning Man Sculpture. Kinesios is focused on participants interacting to experience a place between order and chaos.


\section*{Lunar Fire}
A fire plate of four crescent moons (2 large, 2 small) emit flame all along the outline. The 2 circles are both; an open hole in the plate where the sky is visible, and propane outlet similar to the crescents, but larger, and these will be the push button flame/flood effects. 

\section*{Lucid Lounge}
Lucid Lounge consists of a large covered octagonal PVC framed structure / decorated space with bed and gongs inside intended for sound healing and is not a chill space, but intentional guidance and gong / singing bowl sessions with prior signup.\\
Lucid Lounge will also host several yoga sessions on the platform when no sessions are taking place, overlooking the fields and river.


\section*{Mirrorverse}
I was inspired by the infinity mirror exhibit to make my own infinity box that contained art that would be reflected by the walls and roof. Hanging lights will be an addition at night. Making the floor into a longstanding mirror may be an addition for another year. To assemble the room at the burn will not use any screwing, but rather groove fits and heavy duty toggles making it easier to disassemble and reassemble. At least one of the walls will be made into an infinity mirror.


\section*{Moon Shuttles}
Last year, we were excited to receive a grant for the Moon Shuttles! We are excited to bring out four Moon Shuttles (Heavy duty Garden carts/wagons) back this year, decorated in accordance with this burn's theme A History of Mysteries. The Moon Shuttles are located at the Shuttle Station that will be set up at Greeters. Moon folk can use the shuttles to carry gear to their camps, pick up ice, transport gifts, haul general items around the site, etc. This year we will have two shuttle station, one at the front gate and then the other at our camp.  


\section*{Pieces of Us}
A gallery display of mixed media collage pieces focusing on illness, birth, life, death, love, and success. 


\section*{Pocket Dimension Waystation}
A wall of small cabinets, each containing a tiny dimension inside! Guests are invited to play with the lights and discover ``secret'' interactive components in each scene! There will also be Dimensional Objects on display by the cabinets for guests to look at and play with! The outside of the Waystation will be covered in masks that everyone is welcome to try on and play with. The masks will be gifted away throughout the weekend!  


\section*{Pussy Pagoda}
A feline inspired multi-tiered tower built in the traditions and in rendition of historic Asian culture. An immersive 6 sided base scaffolding structure wrapped in playa-tech design to form a bar like setting which will be host to a hookah and CBD lounge at this years moon. Kittens can climb their way to the second tier perch built from metal pallet racking shelves and more scaffolding which will host a multi-faceted sensory filled exploration and kitten cuddle puddle.

\section*{Tetra Borealis}
Originally built as the entrance tunnel for Love Burn 2019 in Miami, Tetra Borealis is a shimmering kinetic sculpture and tunnel that reacts with the wind. It is made from a net covered in nearly 5000 shimmering strips of dichroic film that sit upon a metal frame. As the wind blows, the 4ft long strips undulate in the wind, changing colors as they move.


\section*{The Bermuda Pyramid}
Join us for an immersive fiber arts flow experience when you come to kick it in the Bermuda Pyramid! It has been known for centuries to trap many souls, so bring a friend or four! Get some flow time, some rest, water, or come and get some perspective laying under our giant crystal pendulum when the space is clear.


\section*{The Cooler}
What's cooler than being cool? Popsicles, duh. Come on down to Spontaneous Combustion [prevention] and reach into the Cooler for a refreshing popsicle, or step your whole body inside and become a human popsicle in our air conditioned cuddle-puddle!  


\section*{The Intention Ascension Invention}
The Intention Ascension Invention will consist of a table with note cards on it and markers/pens for writing on these note cards a wish, fear, goal, problem, or intention that a person has. Others will come and read these anonymous note cards and will be asked to intentionally send positive vibes out into the universe directed at these people who have written on the note cards. Then, they can leave their own note cards. If a person particularly relates to a certain note card and wants to reach out, they can leave contact info or a note of encouragement or advice, whatever they are comfortable with, and leave it in a closed envelope behind the person’s note card so that person can come back to it and read it later. 
 


\section*{The Lost Temple of Magdaluna }
Come explore the Lost Temple of Magdaluna, where you are greeted by strange, yet familiar surroundings. The ancients left clues to the past and the not-so-distant future hidden in the temple walls and moon room. Come create your own lunar masterpiece with the mysterious moon paint.  


\section*{The Lunar Yearbook}
Portrait Studio Capturing the Lunartics of 2019 and Beyond! Individual and camp burn portraits complete with props and superlatives. Feel free to bring your own and wear whatever you like! Check the posted portrait hours of snappification. 


\section*{The Moon}
..... meow.


\section*{The Oracle Is...}
You are invited to take a seat at a Charlie-Brown-like fortune-telling desk with two chairs on either side and a marquis which says "The Oracle is" and a flippable sign that says "In" on one side and "You?" on the other.   Participants can either dispense or receive fortunes, insights and other clairvoyances. 


\section*{The Satin Worshippers Dome}
A lounge space decked out in satin cloth 

\section*{The Visitors}
The Visitors is a flying saucer hovering in the sky over To the Moon, abducting participants wherever it goes. This is a companion piece to the TTM effigy, since it is increasingly clear that aliens (``the visitors'') are the true architects of the Pyramid (effigy). The Visitors will be used as such for a party at the effigy as well as dance and other events throughout the burn. The spaceship will be 16ft in diameter with intelligent lighting, programmed LEDs, a disco ball, and a fog machine all focused down towards the ground. The Visitors will utilize the DPW/Effigy teams' VR forklift, turning it into a mutant vehicle at night. This will allow us to fly The Visitors over anything at the burn, including the effigy.


\section*{The Zoltar Booth}
Come by the Zoltar Booth and have your fortune told, make a wish, play Truth or Dare, consult the Magic 8 Ball or just get some good (or bad) advice. Just be careful what you wish for... don’t ask for anything too ``Big''. 

Be on the lookout for such infamous wish/luck bringers as the mystical Zoltar, Aladdin’s Genie of the Lamp, a large white Rabbit (this isn’t ``Harvey''), or one of those pesky Leprechauns as they man the booth and wander the event. Catch them for all kinds of surprises ((no tackling please – wish bringers are fragile and startle easily)).

\{Would you like to participate? Can you tell fortunes, belly dance, or perform cool tricks? Do you have a snazzy outfit and would you like to be Zoltar for an hour or two. Message me (\url{ouijacat.tothemoon@gmail.com}) or sign up at the Booth.\}
 
\section*{The Space Dome}
Our Dome is a social environment for people to find shelter from the sun and make new social connections while enjoying the comfiest of social areas. The floorspace is filled with stuffed animals and other soft cushioning to give hippies a place to kick off their shoes and fall into a pit of plushness. Around the edges are chairs for those who wish to retain their foot-prions. The framework of the dome has reflective mylar stretched over it for protection from the sun and rain, and is lined with LED strips from top to base. It's the perfect spot to take a break from the noise outside while surrounded by a shifting spectrum of colors shooting in all directions. It's a great place to relax, chat, or sleep without getting bored.


\section*{To The Moon Postcard Photo Frame}
The To The Moon Postcard Photo Frame is a 6' x 10' decorative frame mounted on poles with a moon surface to sit on along with a camera / phone stand set at a measured distance.  This will enable people or groups of people to take timer set photos from their own devices so everyone is included in the shot.  The background of the image will be the property.   


\section*{Tree Star City}
Multiple tentsile tents, hammocks, and extra large dream catchers all hanging in the trees on the hill.


\section*{Truffula Tree Grove}
Ten brightly colored truffula trees, inspired by Dr. Seuss' The Lorax. With fiber optics and led lights, the trees light up the night and provide a strange, beautiful space for burners to lounge on mats and relax. 

\section*{Web Lounge}
Giant crocheted rope web hammock. Comfortably holds a dozen people. Nice chill space with lots of fans in day and lit up at night.
This year is going to be extra special. In the past I was bound to the colors that home depot would provide. Since I have learned the art of making rope. I have all the colors to play with now. With a little help This year will be my first true masterpiece. A mandala with purple, blue, teal, green, yellow , red!!


\section*{Wormhole}
Wormhole is an interactive led light tunnel. It’s intended placement is in between effigy and temple as clear bright pathway between the two. We’ve played with this idea in 2017 and at a small scale was a great success thanks to Gabi! The Wormhole is 40ft long on an elevated platform with a continuous 1” programmable led poly tube that is 400 ft long swirling around you as you make it from one end to the other.


\section*{You are Water. Our inner Yemaya. 8th Ocean Body.}
A sculptural interactive art installation homage to our ecosystem in balance, made
from orgonite talismans paying tribute to bio-remediation. An art piece to honor the interconnection between life and the heavenly bodies of the Earth and the waters, to encourage people to respect water.

\newpage
\section*{Draw Your Own Art Here!}