\chapter{In-Flight Procedures}

% This is true if only doing the flight manual, not the pre-flight
% \ifisflight
%   % This one page needs to be one column to look right, even
%   % in the flight manual, proper.
%   % failed experiment to add thumb guides
% %   \addthumb{Welcome}{}{white}{black}
% \putchapterthumb
% \fi


Once you're at \gls{ttm}, you'll want to keep gate hours in mind (if you leave), and before you finally pack up to go to your rest-of-the-year home, please take a moment to read through our takeoff procedure!

\section*{Gate Hours}

\textbf{No vehicles will be allowed in after sunset! No moving vehicles \textit{period} inside the burn when it's dark - so if you get there right before sunset, you better get in, unload your stuff, and get right back out to parking ASAP. This is for the safety of everyone at the burn!}

Any vehicles that arrive after sunset will be redirected to parking, where we may or may not have a golf cart to help you carry some stuff in --- but don't count on it --- use that Radical Self-Reliance!

\begin{table*}[h!]
\footnotesize
\centering
\caption{\Gls{ttm} \gls{gate} hours}
\label{tbl:gatehours}
\begin{tabular}{@{}lll@{}}
\toprule
Wednesday & 6/22/2022 & 12pm--midnight CST                                    \\ 
          &           & \textbf{Theme Camp Early Entry Only w/ Pre-Registration }\\
Thursday  & 6/23/2022 & 10\am--12\am CST, general admission                                   \\
Friday    & 6/24/2022 & 10\am--12\am CST, general admission                                    \\
Saturday  & 6/25/2022 & 10\am--6\pm CST, \textbf{no admission after 6pm for rest of event }\\
Sunday    & 6/26/2022 & 10\am--6\pm CST                                    \\
          &           & \textbf{Departing Only}                                  \\
Monday    & 6/27/202 & 8\am--12\pm CST                                    \\
          &           & \textbf{Departing Only}                                  \\ \bottomrule
\end{tabular}
\end{table*}

\section*{Re-entry Procedure}

% \todo[inline]{Still awaiting guidance on this policy.}
% \textbf{There is no after hours entry without pre-arranged permission.  Crew arriving at the site outside gate operating hours will be turned away.  No crew is permitted to wait on the property until the gate opens.}

% Please contact the \gls{bod} via \url{connect@tothemooonburn.com} well in advance of the event to work out options if long-distance travelers cannot arrive while the gate is open.

% For the safety of other patrons and to preserve the integrity of the experience, \textbf{no} coming and going at leisure is allowed after checking in.  Exiting and returning \gls{ttm} are reserved \textbf{for medical and emergency reasons only}, and must be communicated to and cleared by the Gate Lead prior to leaving.

% Theme Camp supply runs are possible Wednesday -- Friday before 10\pm \textbf{only}. Before leaving, \textbf{check at the gate} if a pass is needed. The Gate will check with \Gls{el} on call and a re-entry lanyard will be issued at \gls{el} discretion.

% % If you forget something and need to ``make a run to the store'' talk to a team / event  / gate lead and we can grant Re-Entry if you combine your trip with one beneficial \gls{ttm} and the community at large.

\textbf{No after-hours entry without pre-arranged permission!}

Arriving outside of these hours will result in being placed in our waiting lot outside the event gate until the it opens the next morning. If you foresee that you will arrive after gate hours, let your \gls{tco} or the \gls{eventleads} know ahead of time. Security will meet you at the \gls{gate} and will radio an Event Lead on shift to come check you in if possible.

We understand many of you travel long distances so if this presents a problem for for you, email us plenty in advance at \url{connect@tothemooonburn.com} so we can look at options

For the safety of other patrons and to preserve the integrity of the experience, NO coming and going at leisure is allowed after checking in. Exiting and returning To The Moon are reserved for medical and emergency reasons only and must be communicated to and cleared by Gate Lead prior to leaving. Other than that, please refrain from leaving and returning at leisure as you will not be able to get in.

% This is covered elsewhere: ANYONE WHO BREACHES THE SAFETY PERIMETER OF THE BURN MAP AT ANY TIME DURING THE EVENT, WILL BE REMOVED FROM SITE WITH NO RE-ENTRY.

We understand the property is huge and getting around can be a bit challenging --- however, once your car is parked it has to stay parked --- \textbf{NO DRIVING AROUND DURING THE EVENT IS ALLOWED!}

Thank you for understanding!


\section*{Takeoff Procedure}
\subsection*{Leave No Trace}
\Gls{ttm} follows the \gls{lnt} principle (see \gls{tenprinciples}, page \pageref{tenprinciples}). Please take all your belongings, trash, and \gls{graywater} with you and leave the site in a better shape than you found it.

\subsection*{Takeoff Launch Window}

\Gls{ttm} officially closes at 11:59\pm CST, Sunday, June 26th.  All crew must vacate the site by 12pm CST, Monday, June 27th unless given explicit prior permission from Theme Camp Late Departure.

Vehicles can be driven on site on Monday to pack up. In case of inclement weather, a no driving / limited access policy to site will be implemented. Be prepared by bringing your own cart / wagon to transport gear out and to your vehicle.
\Gls{love} will be able to assist with shuttling gear to parking. 
Vehicles can \textbf{not} be parked alongside road to do so, but only be lined up at gate about 10 at a time.

Please look for announcements at \Gls{cockpit} / \Gls{gate}, as this policy may slightly change, depending on situation. 

\input{common/resources}