%
% Part of the reason why we go to burns, AMIRIGHT?
%

\chapter{Art}


\begin{multicols}{2}


\section*{Funded Art}

\subsection*{3rdeyeluminart by Loren shaw}
        Live painting

\subsection*{Adrift' Shuttle by Johnie "Five" Waddell}
         Transporting people to the drop off point for floating the river by day and will be         an amazing LED art car by night: makes for a great companion to any stage.        


\subsection*{Appalachian Art Lab by Stacy Kraft / Running Doe                       }
Hi! Running Doe here! Come experience the element of neon visually represented through a series of black-light reflective abstract art. We are bringing back the Make-Your-Own-Dream flags for the Temple Burn and will have a table set up with fabric and markers for you to come and create as you please throughout the weekend. Depending on the weather and humidity, we might do an art demo on Friday. Much love, Running Doe


\subsection*{Art Carts What What! by Alannah "sole" Tomich        }
Have you arrived on the moon and want to start enjoying burny art projects but still have to unload and build your camp? Have a lot to haul to get your camp packed-up but your car might get stuck in the mud? The Acrodesiac Lunartics (AcroYoga camp) presents ArtCarts, decorated mobile art pieces for all your camp gear transport needs with heavy duty wheels for the mud. To help you arrive on the moon with ease and color and burner spirit. Come check out our elemental designs. Let’s be gentle on the meadow (leave no trace) and come borrow an ArtCart from our stand. 


\subsection*{BLAST OFF by Caitlin and Sassy Noodle                }
Ooooo we flying in the spaceship, back to the basics, back to the matrix. Strictly constructed of cardboard and awesomeness. Crawl in through the space hole and be blasted off into another dimension. My spaceship is equipped with comfy, cushy, pillows to sit and relax and gander up at the nicely painted glow in the dark stars that’ll make you feel as if space really is surrounding you. Feel the interstellar vibes from the ambient music that will be playing throughout the night when the sun goes down and the moon comes out. Come BLAST OFF.        
                
\subsection*{The Bizarre Bazaar        by Robert Blew        }
"A theme camp featuring a 20 ft tall teepee in the center that provides a cozy space for wandering burners to take respite from the stress of the burn and smoke hookah in a comfortable lounge. Nearby, they can enjoy the booths that make the "Bazaar" part of our camp, including our "secret shop" for undisclosed curiosities, art booth for the viewing of camp-member-made trippy art, a distillery for a sampling of flavored moonshines made by camp members, and an artisanal coffee bar for a selection of espressos, cold brews, lattes, and the like.


\subsection*{The Blue Box by Jessica Logan                 }
        A full scale replica of the Doctor Who TARDIS.


\subsection*{The Booth Fairy by Elle Erickson                }
        Super fantastic and interactive Free advice booth




\subsection*{Booty Prints by Ashley Humphries                        }
Booty beautification imprintation is being brilliantly brought to you by Ashley the asscommander of Alcoholic Alliterators. Stop by our booty beautification booth to have your booty beautified and then captured creatively on a flat medium to take home with you. The booth will be open at choice times to accommodate your accentuated assets. So come by, grab an alcoholic alliteration and print your posterior.


\subsection*{The Brownie Brothel by Catherine Nguyen (no burner name... yet)        }
The Brownie Brothel is the leading purveyor of from-scratch, gourmet, artisan desserts to the Georgia Burns, and we're excited to bring our sweets to To The Moon for the first time. As done for past events, we plan to bake and distribute a wide variety of tasty, ranger-safe baked goods to all and sundry, including those with dietary restrictions. In addition, our goal is to use baked goods to teach the community lessons about engaging in healthy consent habits.


\subsection*{Clean Hippies Taste Better         by Erick Bixler/ MavErick Cadabra         }
Come wash away your woes at camp “clean hippies taste better”. We will be providing 2 hot/cold water showers, hot/cold pools, and a chill dry space to change and regroup before you blast off around the moon again. Join us Friday night and sat night at 1am and again Sunday at 10\pm for our shower disco party. All the steamy showers in one big room for 2 sweet hours. Get clean or get weird. Just clean up the mashed potatoes when you’re done.         


\subsection*{Clouds on the Moon by Dorne Pentes/ Awesome                }
A small, experiential moon-like space consisting of LED clouds moving and changing to music. Housed in a small geodesic dome with pillows and blankies to lie on and watch it move.


\subsection*{Connecting Through Eye Contact by Ashley Maynard (Bones)                }
Hang out with a stranger, or a friend, and maintain eye contact for 1 minute.  Feel their spirit within you and share your spirit with them.  Re-establish the human experience and enter the windows to the soul.         

\subsection*{Countdown by Aaron Averill}

Enter the capsule. Experience the universe falling away as you are bathed in rhythmic changing lights. Meditate and look inward, or enjoy with a friend or two.


\subsection*{Cosmic Express by Willow Gaia and Kris Totillo}
Float along with the GOATs! Ride on the majestic cosmic farty cloud. Greatest of all Time; Moon tours and exhibitionists daily!


\subsection*{Cutie Clinic by EVP Grace Tsaritsa                        }
Oooo pretty pastel colors! But wait...this is kinda creepy. That's the whole point of our happy hospital, taking uncomfortable topics like chronic and mental illness and making them refreshingly kawaii. This interactive installation is based around the Japanese street style Menhera, also known as yumekawaii or "sick cute".We invite you to look at our magical pieces, make your own get well soon cards, or hang out in our cuddly stuffie pool. Remember: your health should be your first priority!


\subsection*{Dancing Fungi by Jeremy Bourque                }
An interactive art camp/mushroom fairy garden consisting of a large mushroom cottage made entirely out of recycled materials, with a repurposed satellite dish for a roof, a light up mushroom garden, mushroom art, a creation station for attendants to make their own arts and crafts, and speakers and lights throughout. The cottage will have various features, such as a dj booth, dance floor and a stripper pole, and lots of hidden surprises.


\subsection*{Dream Scarf by Nicole Sholtis                 }
I'll be wearing a special scarf made of small pieces of paper and safety pins. All you have to do is write down a hope, a dream, a goal, a wish... roll the paper up and pin it to the scarf that will burn with effigy.        


\subsection*{Dream Weaver Manifestation Station by Holly Hamel - Mother Superior        }
"We all have our own life to pursue, our own kind of dream to be weaving, and we all have the power to make wishes come true, as long as we keep believing."   -- Louisa May Alcott      
The Dreamweaver Manifestation Station is a giant dreamcatcher interactive art piece that works through the Law of Attraction. You, the Dreamer, are offered an opportunity make an intentional wish for your heart’s truest desire. The Intender’s Circle will add our powers of manifestation to your dream, with the caveat that all is in the best interest for YOU and your journey. Be sure to send feedback of your manifestations coming true to holly.mothersuperior@gmail.com!


\subsection*{Element Altar and Affirmation Station by Rachael Peak                 }
A peaceful small place with an altar to the elements in the same space is an affirmation station. Words are powerful. Hundreds of artsy and laminated positive quotes, mantras and affirmations will be in a big treasure chest for burners to look at, or to take one to help then with their day/life. Also, there will be a creative spot to write down manifestations that will likely be burned at the end.


\subsection*{Elemental Pillars        by Andrea Long (Andi Glytch)        }
The EleMENTAL pillars will tower above and look over us all, turning nature into interactive visual art! Our four elemental symbols will stand tall for most of our journey and eventually burn with the fire of the gods!        


\subsection*{ElemenTapestries by Aaron Robbins                }
Tapestries made out of old sheets from thrift stores. We use a technique that we call faux batik. We use washable glue to create an image then paint it with acrylics. The fabric is then washed out, so that anywhere there was glue remains white. The resulting image looks like batik, tie dye and stained glass.


\subsection*{Envision by Sidhe •. Natalie Starr Mudd                }
A Temporary Kinetic Sculpture and Sacred Space made of thousands of holographic palettes. These cascading holographic shapes dance and sparkle in the breeze, creating a mesmerizing iridescent shimmer, similar to light reflecting off rippling water, or sunlight dappling through the leaves. Come and sit a spell. <3        


\subsection*{Eons of Neon: The Fluoresciverse by Tyler Key, TzKey ( Beast)                 }
A giant, 360 degree, neon, fluorescent, black-light-reactive mural. Imagine standing in a circular room, the sky is your ceiling, the walls are 8 feet tall with mesh screening, covered in murals, bathed in black light, and in the middle of the room are blankets, pillows, inflatable couches and chairs, and bean bags.


\subsection*{The Euphoria Temple by Patrick Murphy        }
        We built the temple for Euphoria, but unfortunately Euphoria didn't happen :( We         want to share our temple with burners, and hope to be able to burn it at To The         Moon.        


\subsection*{Feathered Ear Cuff Crafting Workshop by Pralla de la Torre aka Le Klo                }
Come see us Friday and Saturday to make some killer accessories over at Memento Trio! Bring feathers, beads, or wire if you want! We are gonna craft it upppp! Special thanks to Victoria for helping me hash out the details on this process!


\subsection*{Flower Crown Workshop by Bethany Stonestreet - Mother Superior        }
        Make your own flower crown from fresh, real flowers. Saturday from noon-2p.


\subsection*{Fly me to the Moon }
        A large aerial rig decorated with lights.        


\subsection*{Forever Flowers by Holly Ross                   }
"Forever Flowers” is a beautiful recycling effort that started out as a simple yard art project.   The flowers are made of metal cans, plastic water bottles, lids, etc, and are then painted with bright colors.  This cheery installation aims to bring awareness to the importance of recycling - each flower is a visual representation of a piece of “trash” that will not end up in a landfill or the ocean.  The collection also serves as a haunting reminder of how much trash we create individually. I hope to inspire others to view one-time use packaging as valuable material that can (and should be) reused in creative ways! 


\subsection*{Fricken Laser Beams by Larry Kresse        }
Beams of light that will scan across the tree line at a speed such that humans only see pulsating planes of multicolored light, extending into the horizon.         


\subsection*{Genizm's Manifestation of Light by Genizm (Gurudev and Klay.Ra)                }
"Hello! Here's a quick bit about our art:


   * – GxR's The Manifestation of Light – *
             fri and sat after dark


-> electro jamz by Genizm + vocal improv by Klay.Ra |
-> co-creative audiovisual experience with LaZeRs   | 
-> we invite you to come jam, boogie, or just be    


\subsection*{Heart Melt Café by Katie Gentner "Kitty"                 }
Share a sweet and refreshing ice cream sundae with a new person! To participate take a number and wait to be served! Feel free to join the audience and witness all of the heart melting moments! 


Open Daily: 1-2:30pm, and 7-8:30pm


(Lactose-free vegan ice cream available upon request.)


\subsection*{Hey Y'all: Ain't Yo Mama's Front Porch by Lauren Yanochik and Blake Dunaway                }
The burner version of a good old fashioned front porch for your enjoyment. We will have a bar that serves all the sweet tea you could want and more, all the southern snacks we grew up on, and music of all genres from the great state of Georgia; we will even try to accommodate requests. We will have an illuminated marquee that will list our featured drinks and snacks daily. Come sit with us, either under the porch surrounded by flowers and candles, or by our fire, and share your best "southernisms" on our interactive art project which will consist of a free-standing three panel display blank map (because we also wanna know where y'all from). Sharing a little southern comfort is our goal, and we hope to see all y'all on the porch!


\subsection*{Jellyfish Umbrellas and Flying Squids!        by Elaine Pastor                }
We have electroluminescent jellyfish umbrellas for night use and we are purchasing large jellyfish kites to fly mid-day with a group squid/octopus/jellyfish field frolicking. The umbrellas will be available for others to use and return.        


\subsection*{Lumina by Katie Herman                }
Concentric circles of multi colored luminaries to create a peaceful, calm space for wandering and relaxation at night.


\subsection*{Mehndi Moon SPAce Station by Peaches (Dawn Strickland) and Emi Piez                        }
Divine Goddess Cosmonauts aiding you in your space travels sounds like a stellar dream… come let us make it come true at the Mehndi Moon SPAce Station. Passing astronauts will feel right at home in our antigravity chairs and chaise lounge as they breathe in the aromatic atmosphere within the SPAce Station. The Station will provide several amoonities while aiding those extraterrestrials bravely participating in the Dream Weaver Manifestation Station. Nebulax with our selection of essential oil mists and cooling sarongs. Have your celestial body decorated with henna designs and have your celestial toes painted with paint that glows. Feeling lost in space? We all are, but at Mehndi Moon SPAce Station we will jettison you into a new orbit of planetary pampering.


\subsection*{Memento Serenous        by Niklas "Unicrash" Gahm           }
A burn is a peak of Eristic Energies as we are swept up in the delightfully energetic cavalcade of art, with rare moments of self-preservation and calmness at the temple. But what if we could collectively generate a sound or collection of sounds that center us in the non-silence? SINGING BOWLS. SO MANY SINGING BOWLS. This is an installation entirely focused on the clarity and crispness of a sound delightful. We do not know where this sound may take us, but it can serve as a centering call to rally our spirits as we grow weary with exertion in the expanding exploration of a burn unknown.


\subsection*{The Oracle Is... by Ian Rhett                }
An unassuming "Charlie-Brown" desk with two attached chairs and a (solar-powered) illuminated sign that says "The Oracle Is..." and a flippable "In/Out" beneath it invites anyone to be the Oracle and to dispense Oracle-style futurisms. The desk will be moved throughout the event and will, at one point every day, be staffed by the artist, channeling The Oracle.


\subsection*{Paint by Burners by Olivia Holladay                }
Come paint on the canvases! Free range to paint whatever you want! Add to what other burners have started! Lay the foundation of the master piece that will be added to every burn!


\subsection*{Patchwork Tee Pees by Rachael Marshall                 }
I created Patchwork teepees to bring special energy to the space, experience special moments with the people around me, and to create space to open people up and be free to express themselves through the beauty of art. The traditional teepee was not only an efficient structure, but also a symbolic expression of humanity’s relations with the natural and spiritual worlds. Especially in the case of ceremonial teepees, the process of obtaining hides and poles was and is shaped by prayer and ritual guidelines. Symbols and story drawings were often painted on both the interior and exterior of the teepee, and these drawings were often the expression of visionary experiences. Like the Buddhist stupa or the Hindu mandir, the space created by the teepee is itself symbolic of the wider cosmos: time and the seasons, space and the four directions are associated with the circular floor space of the teepee. In its circle are structured many of life’s activities, from the most mundane to the most sacred. The circle of the teepee is a profound symbol of the interdependence of all of life. I have built the teepees for everyone to come and create space in and share with everyone else to collectively build energy that will grow and resonate through the burn.


\subsection*{Perception Pyramid        by Bryan Bell        }
"Oh, we flood your eyeballs, over, overload your, uh, your earballs, I give you patterns and swirls of color, and, uh, makin’ you feel better and better, yeah, the power of using light to, uh, to enhance consciousness and alter consciousness is the tricks I’m using now, and, so far, they’re legal." -Tim Leary                




\subsection*{Pop        by Kent Davis   }
        A place where volunteers can come get a little coffee have a bite to eat daily!         


\subsection*{The Pussy Palace        by Sara Wright / KC Lepp        }
We will be providing a Playful Kitty Fun-house for all ages. The structure will include:
- Rooms you can crawl through
- Giant oversized cat toys (ex: giant bubble wands, rubix cubes)
- Large slide designed as a cat tongue coming out of a cat head
- An infinity mirror room with furry walls
- Porch lounge area
- Color changing light features
- Rope net
- Covered cuddle puddle pit room
- Scratching and massage post




\subsection*{RV Life by Kimberly Lindemann/Jade                }
A newly remodeled motorhome “open house” where there will be tours and talk with burners about minimalism, downsizing, and how to get started. 


\subsection*{Space Dome        by Rania Glass / Scarlet        }
A temperature-regulated "chill space" for wayward action hippies to relax, make conversation, and cuddle with our assorted floofs under the watchful eye of the Octopoolpus.        


\subsection*{Sherpa Guided Meditation and art journey by Merri Benham         }
Art booth and night time guided meditation to inspire your evening's journey with awareness and love.


\subsection*{Star City by Trinity White and John LaCount (Sphinx and Teddy Bear)                Tree        }
An exploratory space within the trees made out of several tentsiles and sacred geometry hoop art.


\subsection*{Survival Guide by Piprrr, Raptor, and Bones}

You're looking at it.  ;)

The \gls{survivalguide} is not just intended to inform --- to give enough information for crew to plan and prepare as well as to navigate \gls{ttm} --- but is also our art contribution to the burn.  We hope you enjoy it as much as we enjoyed putting it together for all of you.



\subsection*{Swing, swang, sung by Evans Manrique                 }
        Swings for adults to feel like kids again.        




\subsection*{To The Moon Photo Booth by NativeEye Photography                 }
Dawn the neon! Jump in your space suit!
Grab your crew get ready for blast off >>>>>TO THE MOOOOOONNN!
You and your team are venturing to the moon to collect samples and protect each other inside my blacklight moon landing photo booth!
Grab your space team come on down to the burning yacht club camp! Grab some props and samples and jump in the booth for photo shoot fun. Bring a phone for me to snap so you can share with your crew!


\subsection*{Under the Stars by Gene                         }
Visual projectors of stars under our cool stretch tent. Come hang out at The Burning Yacht Club


\subsection*{Where my Beaches At?! by Aaron Shugart-Brown and Dorothy Verbick}
This interactive art installation is a beach style double seating chair elevated at about 12 ft off the ground, complete with plenty of amenities that will bring the attitude and playfulness of the beach TO THE MOON. Imagine yourself watching the “ocean” (river) of people mull about, throw down your rescue rope and make the buddy system come alive. Styling out under the umbrella our beach tower comes with all the fun in the sun that you would ever dream up! Complete with Zinc Oxide, Mounted Beach Umbrella, Hand Crank Weather Radio, Bulletin Board (missed connections, lost and found, general information), Megaphone, Life Preserver, Costume Chest, and Binoculars. Take notes on the clipboard, Spot a new friend, and throw the lifebuoy - we are proposing a fully immersive experience that promotes taking on the “responsibilities” of being a lifeguard at a burn. The 11 principles and a map will be posted on the structure. These stations can also be used by the Rangers for safety purposes if needed.                        


\subsection*{Yarn Doll Moon Spirits by Thomas O’Connor and Caleb Franklin                }
A cozy interactive art installation with a make-your-own yarn doll crafting station for others to take and leave dolls, make and gift yarn creations. There are plans for large rope scultptures imitating yarn dolls surrounding a large area with rugs, pillows, piles of yarn, string, safety scissors, beads, and charms to create. there will be walls where you can hang them, along with long may-pole like strings to clothespin dolls for gifting tree purposes.

\section*{Funded Burn Art}

\subsection*{Euphoria Temple by Patrick Murphy and Katie Herman}

Friday night Euphoria Temple Burn in dedication of Larry Harvey "The Man in the Hat".

This Temple was originally created for Euphoria this year.  When Euphoria was canceled, the stars aligned and it found its place at To The Moon.  It houses dozens of pieces of laser cut art created by the Georgia burn community, creating an engaging mix of light and shadow once the sun goes down.  

\subsection*{Sunday TTM Temple by  Michael "Lunar" Luber and Matthew Horner}
We would like to introduce the ElemenTemple! This is where Fire, Water, Earth and Air, join with the Spirit, brought together through an eclectic collaboration of art! This will be in the lower level. 
From the ground to the sky will be the connection of the creation, the universe and all, sending a beacon of light into the sky.
The ElemenTemple burn will be at dusk/dark:30 Sunday evening, so please plan on hanging out to send her to the skies and back.

Please feel free as always to write your dreams and wishes, anything you want to take in or let go of, and if you would like to keep them private, there will be paper to write on that will remain confidential, that I will hang in the temple before we send it up.
See ya'll on the MOOOOON!!!!

\section*{Effigy Burn by Ezra "Everywhere" Bowers and Josh Boyer}
\bod[inline]{Needs description}

 

\end{multicols}