\section*{Crew Equipment}
% Things to do / pack before leaving
\gls{ttm} is an exercise in radical self-reliance.  This means bringing everything you are going to need, which includes food, water, shelter, any medications, and hygiene products.  You must take responsibility for your own well-being and survival.  Do not expect the community to take care of you.  Though there are EMTs on site, they are only an emergency resource, so do not rely on them for basic over-the-counter medications.

\subsection*{Crew Inventory Checklist}
Below is a list of items we suggest you bring with you.  A burn requires a certain amount of preparation to be able to sustain you for 4--5 days of camping with minimal amenities. Please come prepared.  While this isn't the Playa, the nearest store is a bit removed so pack what you need and extra.  

% The following are checklists for items that are recommended to bring to ensure maximum likelihood of survival and an otherwise hoopilicious time.  The first checklist is for items that crew should bring; the second are for nice to have items.

\subsubsection*{Must Haves}

\begin{multicols}{2}

\begin{checklist}
	\item \textbf{A valid, state-issued} photo ID
    \item Your printed ticket
    \item Emergency contact
    \item  1 gallon of water per person per day for drinking, washing, and food preparation
    \item \textbf{Negative COVID test} per our COVID policy (see page \pageref{covid-policy})
\end{checklist}
\end{multicols}

\subsubsection*{Strongly Recommended}

\begin{multicols}{2}

\begin{checklist}
	\item tent
    \item sleeping bag and/or bedding
    \item blankets
    \item tarps
    \item food for everyone in your group for length of stay
    \item sufficient ice for duration \footnote{Some stores also sell dry ice. However, be sure to wrap dry ice in towel for further insulation.}
    \item any necessary medication
    \item any necessary medical equipment (e.g., CPAP)
    \item epi pen
    \item if needed, contact lens supplies
    \item first aid kit
    \item sunblock
    \item insect repellent
    \item deodorant
    \item single ply toilet paper \footnote{The port-a-potties only get serviced once a day, and may run out of toilet paper.}
    \item paper towels
    \item baby wipes or moist towelettes
    \item towels
    \item biodegradeable body washing soap
    \item biodegradeable dishwashing soap 
    \item \gls{graywater} container and funnel \footnote{A cat litter bucket works well as gray water containment.}
    \item garbage bags, recycling bags, and tools for \gls{moop} containment
    \item flashlights, spare batteries, headlamps, LEDs for your camp  (solar powered recommended) 
    \item reusable cup or bottle \footnote{Many camps offer drinks, but do not provide cups.  A cup with a carabiner is ideal.}
    \item reusable utensils and dinnerware \footnote{Many camps offer food, but do not provide utensils or plates}
    \item condoms
    \item pocket knife
    \item hammer
    \item sunglasses
    \item rain hat / rain gear / umbrellas
    \item chargers for phones and medical equipment
    \item gifts
    \item a loving and open mind
    \item \hrulefill
\end{checklist}

% * <mcoletti@gmail.com> 2018-05-08T17:10:50.436Z:
% 
% >     \item \hrulefill
% Possibly add more of these to fill out the page.
% 
% ^.\

\end{multicols}

\subsubsection*{Optional}

\begin{multicols}{2}

\begin{checklist}
    \item swimsuit
    \item water shoes
    \item inner-tube
    \item can or bottle opener
    \item simple toolkit
    \item rubber mallet
    \item rope, string, zip ties, duct tape
    \item sewing kit
    \item portable metal ashtrays \footnote{Mint tins work well for this purpose.}
    \item lawn chairs
    \item pop-up shelters, pavilions, or other forms of portable shelter
    \item ice chests
    \item camp cooking stove
    \item fuel for stove 
    \item fire bowl
    \item fire wood
    \item fire extinguishers
    \item fuel and safety gear for fire performance
    \item watertight protective bags \footnote{For cameras and electronics.}
    \item generator
    \item tea and/or coffee
    \item coffee pot, tea pot, or french press
    \item earplugs
    \item musical instruments
    \item parasols
	\item spray bottle of water for keeping cool
    \item pasties 
\end{checklist}

\end{multicols}


\subsection*{Prohibited Items} %\todo{themed name?}
Please do not bring \textbf{any} of the following items:

\begin{multicols}{2}
\begin{itemize}[noitemsep]
	\item Handheld lasers --- they are too powerful to be safe
    \item Fireworks --- unsafe use of fire and creates \gls{moop}
    \item Chinese/fire lanterns --- uncontrollable, flaming \gls{moop} 
    \item Pets of any kind (please see pets policy on page \pageref{sub:nopets})
\end{itemize}
\end{multicols}
